Why Donors Donate?

### 2020-09-02 analysis/05_market_simulator.Rmd
Changing inputs cont.

# Need to Fix
selectInput("p1_national_news",
         label = "Follow national news:",
         choices = c('Multiple times a day',
                     'Every day',
                     "Once a week",
                     "Hardly ever",
                     "Never"))

>>>>

# Need to Fix
selectInput("p1_national_news",
         label = "Follow national news:",
         choices = c("Atleast once a day",
                     "Once a week",
                     "Rarely"
                     ))
